---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r environment, result='hide',echo=TRUE}
env=Sys.setlocale("LC_TIME", "English")
library(data.table)
library(dplyr)
library(tidyr)
```

```{r load,echo=TRUE}
library(data.table)
library(dplyr)
library(tidyr)

zip_name <-'activity.zip'

if (!file.exists('activity.csv')){
  unzip(zip_name)
  }
dt<- fread('activity.csv',na.strings='NA')

```

## What is mean total number of steps taken per day?
```{r calc_mean}
steps_daily <- dt %>% 
  group_by(date) %>% 
  summarise(steps=sum(steps,na.rm=TRUE))
# histgram plot total steps pattern
with(steps_daily, hist(steps))
mean_step <- mean(steps_daily$steps)
median_step <- median(steps_daily$steps)
```
Above is the total number of steps taken per day.   
The mean value is : `r mean_step`.   
The median value is : `r median_step`    

## What is the average daily activity pattern?
Make a time series plot (i.e. \color{red}{\verb|type = "l"|}type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r tsplot, echo=TRUE}
#avg_dt <- dt %>% group_by(date) %>% mutate(average=mean(steps))

with(_dt, plot(steps~date,
              type='l',
              xlab='5 minutes interval',
              ylab='average number of steps'))

```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
